---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# autorecipes

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/dzhang32/autorecipes/workflows/R-CMD-check/badge.svg)](https://github.com/dzhang32/autorecipes/actions)
[![Codecov test coverage](https://codecov.io/gh/dzhang32/autorecipes/branch/master/graph/badge.svg)](https://codecov.io/gh/dzhang32/autorecipes?branch=master)
<!-- badges: end -->

The goal of `autorecipes` is to automate my weekly recipe planning (and practice using OOP in `R`).

`autorecipes` takes care of:

  1.  Creating and storing a database of recipes
  2.  Customizing weekly meal plans
  3.  Generating shopping lists of ingredients

## Installation

`autorecipes` exists purely for personal use and is no longer under active development. If you’d like to install the development version from GitHub you can use the following:

```{r install-dev, eval = FALSE}
devtools::install_github("dzhang32/autorecipes")
```

## Usage

The below example gives a taste of `autorecipes`. If you would like to sink your teeth into a more detailed tutorial, head over to the
[vignette](https://dzhang32.github.io/autorecipes/articles/autorecipes.html).

```{r example, eval = requireNamespace("autorecipes")}

library("autorecipes")

# autorecipes contains an example set of recipes
head(recipes(recipebook_example))

# create a meal plan for lunch and dinner across all weekdays
recipebook <- create_meal_plan(recipebook_example)

head(meal_plan(recipebook))

recipebook <- create_shopping_list(recipebook)

head(shopping_list(recipebook))

```

## Credits

`autorecipes` was developed using `r BiocStyle::Biocpkg("biocthis")`.
