---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# autorecipes

<!-- badges: start -->
[![GitHub issues](https://img.shields.io/github/issues/dzhang32/autorecipes)](https://github.com/dzhang32/autorecipes/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/dzhang32/autorecipes)](https://github.com/dzhang32/autorecipes/pulls)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/dzhang32/autorecipes/workflows/R-CMD-check/badge.svg)](https://github.com/dzhang32/autorecipes/actions)
[![Codecov test coverage](https://codecov.io/gh/dzhang32/autorecipes/branch/master/graph/badge.svg)](https://codecov.io/gh/dzhang32/autorecipes?branch=master)
<!-- badges: end -->

As an unadventurous, by-the-recipe cook, I had accumulated a set of ~25 go-to meals that were cycled through depending on mood, time and what I'd had the week before. Over time, this weekly, manual selection process became repetitive. `autorecipes` was born from this repetition; it automates recipe planning by taking care of:

  1.  Creating and storing a database of recipes
  2.  Customizing weekly meal plans
  3.  Generating shopping lists of ingredients

## Installation

```{r install-dev, eval = FALSE}
devtools::install_github("dzhang32/autorecipes")
```

## Usage

The below example gives a taste of `autorecipes`. If you would like to sink your teeth into a more detailed overview, head over to the
[vignette](https://dzhang32.github.io/autorecipes/articles/autorecipes.html).

```{r example, eval = requireNamespace("autorecipes")}

library("autorecipes")

# autorecipes contains an example set of recipes in recipebook_example
# recipes stored in RecipeBook-class objects can be retrieved using recipes()
head(recipes(recipebook_example))

# create a meal plan for your lunch and dinner across all weekdays
recipebook <- create_meal_plan(recipebook_example)
meal_plan(recipebook)
```

## Development tools

* Continuous code testing is possible thanks to [GitHub actions](https://www.tidyverse.org/blog/2020/04/usethis-1-6-0/)  through `r BiocStyle::CRANpkg("usethis")`, `r BiocStyle::CRANpkg("remotes")`, and `r BiocStyle::CRANpkg("rcmdcheck")` customized to use [Bioconductor"s docker containers](https://www.bioconductor.org/help/docker/) and `r BiocStyle::Biocpkg("BiocCheck")`.
* Code coverage assessment is possible thanks to [codecov](https://codecov.io/gh) and `r BiocStyle::CRANpkg("covr")`.
* The [documentation website](http://dzhang32.github.io/autorecipes) is automatically updated thanks to `r BiocStyle::CRANpkg("pkgdown")`.
* The code is styled automatically thanks to `r BiocStyle::CRANpkg("styler")`.
* The documentation is formatted thanks to `r BiocStyle::CRANpkg("devtools")` and `r BiocStyle::CRANpkg("roxygen2")`.

This package was developed using `r BiocStyle::Biocpkg("biocthis")`.
