---
title: "autorecipes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{autorecipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(autorecipes)
library(magrittr)
```

## Background

As an unadventurous, by-the-recipe cook, I had accumulated a set of ~25 go-to meals that were chosen from each week. Over time, this selection became repetitive. `autorecipes` and [`autogroceries`](https://github.com/dzhang32/autogroceries) are designed to automate this task of creating a weekly meal plan and ordering the required ingredients. 

<br>

## Basic usage

### Example recipes

`autorecipes` defines a `RecipeBook-class` that stores the names and ingredients of recipes. `autorecipes` also includes a set of `length(recipebook_example)` example recipes in `autorecipes::recipebook_example`. 

```{r recipebook-example}

recipebook <- recipebook_example

class(recipebook)

recipes(recipebook) %>% head()

```

<br>

### Set your favourite recipes

`autorecipes` allows users to set their favorite recipes using `add_favourites()` and `rm_favourites()`. This information can be used to determine the subset of recipes that will enter your meal plan. 

```{r set-favourite}

# set the first 3 recipes as favourites
recipebook <- add_favourites(recipebook, 1:3)

recipes(recipebook) %>% head()

```

<br>

### Create a meal plan

`autorecipes` allows you to create meal plan from your `RecipeBook-class` object. For this, you can set the days and meals you would like to plan for and also whether you only want to consider your favourite recipes. 

`create_meal_plan()` can either select recipes randomly (`method = "random"`) or take into account when you have last chosen a recipe for a previous meal plan (`method = "auto"`).

```{r create-meal-plan}

recipebook <- create_meal_plan(
  recipebook,
  which_days = c("Wed", "Thurs", "Fri", "Sat", "Sun"), 
  which_meals = "Dinner",
  method = "auto",
  fav_only = TRUE
)

meal_plan(recipebook)

```

<br>

### Create shopping list

`create_shopping_list()` aggregates all of the ingredients required to make your meal plan into a shopping list. The `filter_method` determines whether to remove store cupboard ingredients (e.g. salt) that you are unlikely to want to order every week. 

The outputted shopping list is designed to then be inputted into [`autogroceries`](https://github.com/dzhang32/autogroceries).  

```{r create-shopping-list}

recipebook <- create_shopping_list(recipebook, filter_method = "minimal")

shopping_list(recipebook)

```

<br>

## Session info

<details>
  <summary>Show/hide</summary>
```{r session-info, echo = FALSE}
library("sessioninfo")
options(width = 120)
session_info()
```
</details> 
