---
title: "autorecipes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{autorecipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(autorecipes)
library(magrittr)
```

# Background

Do you find yourself manually selecting the dishes you want to eat each week? `autorecipes` is designed to simplify and automate the laborious task of picking your weekly recipes. 

# Usage

## Example recipes

`autorecipes` recipes includes a set of `length(recipebook_example)` example recipes stored in `autorecipes::recipebook_example`. Users are enabled and encouraged to add their own recipes, but the example provides a way to use and convey the benefit of `autorecipes` even without a user-inputted, recipe database. 

```{r recipebook-example}

recipebook <- recipebook_example

print(paste0("There are ", length(recipebook), " example recipes"))

recipes(recipebook) %>% head()

```

## Set your favourite recipes

`autorecipes` allows you to set your favorite recipes. This information can be used to determine the subset of recipes that will enter your meal plan by setting `autorecipes::create_meal_plan(fav_only = TRUE)`. 

```{r set-favourite}

recipebook <- add_favourites(recipebook, 1:3)

recipes(recipebook) %>% head()

```

## Create a meal plan

`autorecipes` allows you to create meal plan from your `RecipeBook-class` object. For this, you can set the days and meals you would like to order for. And also whether you only want to use favourite recipes. 

```{r create-meal-plan}

recipebook <- create_meal_plan(
  recipebook,
  which_days = c("Wed", "Thurs", "Fri", "Sat", "Sun"), which_meals = "Dinner",
  fav_only = TRUE
)

meal_plan(recipebook)

```

## Create shopping list

```{r create-shopping-list}

recipebook <- create_shopping_list(recipebook, "minimal")
```
